\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Missing space.

Due to the reasons above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else(Table~\ref{table:median_time}). We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen. However, we noticed that some participants did utilize this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a prefect metric to measure participant engagement.

>>>>

Due to the reasons above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else (Table~\ref{table:median_time}). We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen. However, we noticed that some participants did utilize this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a prefect metric to measure participant engagement.
